Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-03-10 hb.tex
minor typesetting
some fixes

\Mixins{} are declared via the \hbmixin{} command
that takes a module name,
a type variable name and a possibly empty list of \factories{} for that type.
The code between lines~\ref{demo:mixin:mot}
and~\ref{demo:mixin:mot:end} declares a \mixin{} that can turn a naked
type \coq{A} into a monoid, hence we chose the module name to be \coq{Monoid_of_Type}.

The \hbstructure{} command takes in input a name S and a possibly
empty list of \factories{}.
It registers a structure S in the hierarchy placing
any definition specific to that structure inside a Coq module named \coq{S}.
Line~\ref{demo:structure:monoid} hence forges the \coq{Monoid} structure.

@@

\begin{command} to declare a new mixin:
\begin{coqcode}
#\hbmixin{}# Record M T #$f_1\ \ldots\ f_n$# := { .. }. #\hbend{}#.
\end{coqcode}
  Creates a module \coq{M} with a record
  \coq{M.axioms}, which depends on the \mixins{}
  \(\requires{}(\coq{M.axioms}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\), and registers this
  new record both as a \mixin{} and a \factory{}. It also creates a
  \phantterm{} \coq{M.Axioms.}
\end{command}

@@

\begin{command} to declare a new \factory{} and generate new \mixinbuilders:
\begin{coqcode}
#\hbfactory{}# Record M T #$f_1\ \ldots\ f_n$# := { .. }.
#\hbbuilders{}# Context T (a : M.axioms A).

>>>>

\Mixins{} are declared via the \hbmixin{} command
that takes a record declaration with
a type variable name and a possibly empty list of \factories{} for that type.
The code between lines~\ref{demo:mixin:mot}
and~\ref{demo:mixin:mot:end} declares a \mixin{} that can turn a naked
type \coq{A} into a monoid, hence we chose the name to be \coq{Monoid_of_Type}.

The \hbstructure{} command takes in input the definition S for a type
\coq{A} together with a list of \factories{} for \coq{A}.
It registers a structure S in the hierarchy placing
any definition specific to that structure inside a Coq module named \coq{S}.
Line~\ref{demo:structure:monoid} hence forges the \coq{Monoid} structure.

@@

\begin{command} to declare a new mixin:
\begin{coqcode}
#\hbmixin{}# Record M T of #$f_1\ \ldots\ f_n$# := { .. }.
\end{coqcode}
  Creates a module \coq{M} with a record
  \coq{M.axioms}, which depends on the \mixins{}
  \(\requires{}(\coq{M.axioms}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\), and registers this
  new record both as a \mixin{} and a \factory{}. It also creates a
  \phantterm{} \coq{M.Axioms.}
\end{command}

@@

\begin{command} to declare a new \factory{} and generate new \mixinbuilders:
\begin{coqcode}
#\hbfactory{}# Record M T of #$f_1\ \ldots\ f_n$# := { .. }.
#\hbbuilders{}# Context T (a : M.axioms A).
